% =============================================================================
% CONCLUSION SECTION
% =============================================================================
% This section concludes the paper and discusses future work.
% Replace the placeholder content with your actual conclusion.

\section{Conclusion}\label{sec:conclusion}

\subsection{Summary}

This paper presented BlueFort, a novel approach to organizing ACM research papers using 
modular LaTeX files. Our experimental results demonstrate significant improvements in 
compilation performance, collaboration efficiency, and maintainability compared to 
traditional monolithic document structures.

\subsection{Key Findings}

Our research revealed several important insights:

\begin{itemize}
    \item Modular document organization reduces compilation time by 72\% and error rates by 70\%
    \item Parallel development capability improves by 89\% with modular structures
    \item Version control conflicts decrease by 67\% when using separate section files
    \item Overall team satisfaction increases by 78\% with the modular approach
\end{itemize}

\subsection{Limitations}

While our approach shows significant benefits, we acknowledge several limitations:

\begin{itemize}
    \item Initial setup requires understanding of LaTeX \texttt{\textbackslash input} commands
    \item Some advanced LaTeX features may require careful coordination between files
    \item The approach is most beneficial for documents with multiple authors
\end{itemize}

\subsection{Future Work}

Future research directions include:

\begin{enumerate}
    \item \textbf{Automated Section Generation}: Developing tools to automatically 
          create section templates based on paper requirements.
    \item \textbf{Integration with IDEs}: Creating plugins for popular LaTeX editors 
          to better support modular document structures.
    \item \textbf{Template Libraries}: Building a repository of modular templates 
          for different ACM formats and other academic publishers.
    \item \textbf{Collaborative Features}: Adding real-time collaboration features 
          specifically designed for modular LaTeX documents.
\end{enumerate}

\subsection{Final Remarks}

The BlueFort approach represents a significant step forward in academic document 
organization. By embracing modular design principles, research teams can improve 
their productivity, reduce errors, and enhance collaboration while maintaining full 
compliance with ACM formatting requirements. We believe this approach will become 
increasingly important as academic publishing continues to evolve toward more 
collaborative and efficient workflows. 