% =============================================================================
% INTRODUCTION SECTION
% =============================================================================
% This section introduces the research problem, motivation, and contributions.
% Replace the placeholder content with your actual introduction.

\section{Introduction}

The organization and maintenance of large LaTeX documents, particularly those following 
specific formatting requirements like ACM templates, presents significant challenges for 
research teams. Traditional monolithic document structures often lead to version control 
conflicts, compilation errors, and difficulties in collaborative writing. 

\subsection{Motivation}

Current approaches to academic paper writing typically involve single large files that 
combine all sections, making it difficult for multiple authors to work simultaneously 
without conflicts. This problem is especially acute in research environments where 
papers undergo frequent revisions and multiple authors contribute to different sections.

\subsection{Contributions}

This paper makes the following contributions:

\begin{itemize}
    \item \textbf{Modular Organization}: We present a novel approach to organizing 
          ACM research papers using separate LaTeX files for each section.
    \item \textbf{Collaborative Workflow}: We demonstrate how this approach improves 
          team collaboration and reduces version control conflicts.
    \item \textbf{Maintainability}: We show that modular structure enhances 
          document maintainability and reduces compilation errors.
\end{itemize}

\subsection{Paper Organization}

The remainder of this paper is organized as follows: Section~\ref{sec:background} 
presents background information on LaTeX document organization. Section~\ref{sec:methodology} 
describes our methodology for modular document structure. Section~\ref{sec:results} 
presents our experimental results and analysis. Finally, Section~\ref{sec:conclusion} 
concludes the paper and discusses future work. 